The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2014-10-29 tex/CO_drift.tex
update

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{figs/C_O_ratio_2.pdf}
%\vspace{-0.5in}
\caption{C/O ratio in gas and in dust as a function of distance, for a passively irradiated protoplanetary disk (see Equation \ref{eq:diskmodel}). After \citet{oberg11}.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:CtoO}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{figs/drift_timescales_betaS1_gas_acc.pdf}
%\vspace{-0.5in}
\caption{Drift timescale (solid lines), desorption timescale (dashed lines), and gas accretion timescale for $\alpha=0.01$ (dotted lines) as a function of particle size, at three representative locations: the H$_2$O snowline (in blue), the CO$_2$ snowline (in green) and the CO snowline (in red). The horizontal dashed black line shows a typical disk lifetime of 3 Myr.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:drift_times}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{figs/desorption_distance_many_new_2.pdf}
%\vspace{-0.5in}
\caption{Desorption distance as a function on initial particle distance for H$_2$O (top panel), CO$_2$ (middle panel) and CO (bottom panel), for particle size between $10^{-3}$ and $10^8$ cm. The vertical and horizontal dashed lines show the respective snowlines as calculated based on \citet{hollenbach09}. Small particles desorb instantaneously, while large particles do not either drift or desorb before disk dissipation. Intermediate size planetesimals desorb at a fixed distance that depends on the particle size, regardless of their initial location in the disk.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:drift_dist}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{figs/desorption_distance_actual_vs_estimated.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated analytically (when the drift and desorption times are equal) versus the desorption distance calculated numerically, for H$_2$O (top panel), CO$_2$ (middle panel) and CO (bottom panel), and for different initial particle sizes. The analytic and numerical results are in good agreement.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:an_vs_num}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{figs/nH2O_no_acc.pdf}
%\vspace{-0.5in}
\caption{Abundance of water vapor with respect to Hydrogen as a function of semimajor axis, for various particle sizes. Radial drift changes both the shape and the location of the H$_2$O snowline.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:nwater_drift}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{figs/nH2O_acc_wrong.pdf}
%\vspace{-0.5in}
\caption{Attempt to show the abundance of water vapor with respect to Hydrogen as a function of semimajor axis for one particle size, when both drift and gas accretion are included. Obviously wrong.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:wrong}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{../figs/C_O_ratio_2.pdf}
%\vspace{-0.5in}
\caption{C/O ratio in gas and in dust as a function of distance, for a passively irradiated protoplanetary disk (see Equation \ref{eq:diskmodel}). After \citet{oberg11}.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:CtoO}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{../figs/drift_timescales_betaS1_gas_acc.pdf}
%\vspace{-0.5in}
\caption{Drift timescale (solid lines), desorption timescale (dashed lines), and gas accretion timescale for $\alpha=0.01$ (dotted lines) as a function of particle size, at three representative locations: the H$_2$O snowline (in blue), the CO$_2$ snowline (in green) and the CO snowline (in red). The horizontal dashed black line shows a typical disk lifetime of 3 Myr.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:drift_times}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{../figs/desorption_distance_many_new_2.pdf}
%\vspace{-0.5in}
\caption{Desorption distance as a function on initial particle distance for H$_2$O (top panel), CO$_2$ (middle panel) and CO (bottom panel), for particle size between $10^{-3}$ and $10^8$ cm. The vertical and horizontal dashed lines show the respective snowlines as calculated based on \citet{hollenbach09}. Small particles desorb instantaneously, while large particles do not either drift or desorb before disk dissipation. Intermediate size planetesimals desorb at a fixed distance that depends on the particle size, regardless of their initial location in the disk.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:drift_dist}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{../figs/desorption_distance_actual_vs_estimated.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated analytically (when the drift and desorption times are equal) versus the desorption distance calculated numerically, for H$_2$O (top panel), CO$_2$ (middle panel) and CO (bottom panel), and for different initial particle sizes. The analytic and numerical results are in good agreement.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:an_vs_num}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{../figs/nH2O_no_acc.pdf}
%\vspace{-0.5in}
\caption{Abundance of water vapor with respect to Hydrogen as a function of semimajor axis, for various particle sizes. Radial drift changes both the shape and the location of the H$_2$O snowline.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:nwater_drift}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{../figs/nH2O_acc_wrong.pdf}
%\vspace{-0.5in}
\caption{Attempt to show the abundance of water vapor with respect to Hydrogen as a function of semimajor axis for one particle size, when both drift and gas accretion are included. Obviously wrong.} %  (See text for a description of evolution to yet higher masses.) 
\label{fig:wrong}
\end{figure}
